Instructions for developing new pages for the MarineOmics webpage

### 2023-12-16 DRAFT_lncRNA.Rmd
lncRNA stringtie

```{r, engine='bash'}
find ../data/lncRNA/*R2_001.fastp-trim.20230519.fastq.gz \
| xargs basename -s -S1-TP2_R2_001.fastp-trim.20230519.fastq.gz | xargs -I{} \
/home/shared/hisat2-2.2.1/hisat2 \
-x ../output/lncRNA/GCF_013753865.1_Amil_v2.1.index \
-p 48 \
-1 ../data/lncRNA/{}-S1-TP2_R1_001.fastp-trim.20230519.fastq.gz \
-2 ../data/lncRNA/{}-S1-TP2_R2_001.fastp-trim.20230519.fastq.gz \
-S ../output/lncRNA/{}.sam \
2> ../output/lncRNA/hisat.out
```

@@

```{r, engine='bash'}
find ../output/lncRNA/*sorted.bam \
| xargs basename -s .sorted.bam | xargs -I{} \
/home/shared/stringtie-2.2.1.Linux_x86_64/stringtie \
-p 16 \
-G ../lncRNA/genomic.gff \
-o ../output/lncRNA/{}.gtf \
../output/lncRNA/{}.sorted.bam
```

multiqc
```{r, engine='bash'}
cd ../output/lncRNA

>>>>

```{r, engine='bash'}
find ../data/lncRNA/*R2_001.fastp-trim.20230519.fastq.gz \
| xargs basename -s -S1-TP2_R2_001.fastp-trim.20230519.fastq.gz | xargs -I{} \
/home/shared/hisat2-2.2.1/hisat2 \
-x ../output/lncRNA/GCF_013753865.1_Amil_v2.1.index \
-p 48 \
--new-summary \
-1 ../data/lncRNA/{}-S1-TP2_R1_001.fastp-trim.20230519.fastq.gz \
-2 ../data/lncRNA/{}-S1-TP2_R2_001.fastp-trim.20230519.fastq.gz \
-S ../output/lncRNA/{}.sam \
2> ../output/lncRNA/hisat.out
```

@@

```{r, engine='bash'}
find ../output/lncRNA/*sorted.bam \
| xargs basename -s .sorted.bam | xargs -I{} \
/home/shared/stringtie-2.2.1.Linux_x86_64/stringtie \
-p 16 \
-G ../data/lncRNA/genomic.gff \
-o ../output/lncRNA/{}.gtf \
../output/lncRNA/{}.sorted.bam
```

```{r, engine='bash'}
/home/shared/stringtie-2.2.1.Linux_x86_64/stringtie \
--merge \
-p 16 \
-G ../data/lncRNA/genomic.gff \
-o ../output/lncRNA/stringtie_merged.gtf \
../output/lncRNA/*.gtf
```

# GFF compare

```{r, engine='bash'}
/home/shared/gffcompare-0.12.6.Linux_x86_64/gffcompare \
-r ../data/lncRNA/genomic.gff \
-o ../output/lncRNA/gffcompare_merged \
../output/lncRNA/stringtie_merged.gtf
```

multiqc
```{r, engine='bash'}

cd ../output/lncRNA
